\documentclass{beamer}
\usetheme{Montpellier}
\usecolortheme{dolphin}

%\usepackage{graphicx} %For jpg figure inclusion
%\usepackage{times} %For typeface
%\usepackage{epsfig}
\usepackage{color} %For Comments
\usepackage{beamerthemeshadow}
%\usepackage[all]{xy}
%\usepackage{float}
%\usepackage{subfigure} 
%\usepackage{hyperref}
%\usepackage{url}
%\usepackage{parskip}
%\usepackage{multirow}

%% Elena's favorite green (thanks, Fernando!)
\definecolor{ForestGreen}{RGB}{34,139,34}
\definecolor{BlueViolet}{RGB}{138,43,226}
\definecolor{Coquelicot}{RGB}{255, 56, 0}
\definecolor{Teal}{RGB}{2,132,130}
% Uncomment this if you want to show work-in-progress comments
\newcommand{\comment}[1]{{\bf \tt  {#1}}}
% Uncomment this if you don't want to show comments
%\newcommand{\comment}[1]{}
\newcommand{\emcomment}[1]{\textcolor{ForestGreen}{\comment{Elena: {#1}}}}
\newcommand{\todo}[1]{\textcolor{blue}{\comment{To Do: {#1}}}}
\newcommand{\hfcomment}[1]{\textcolor{Teal}{\comment{Henry: {#1}}}}
\newcommand{\thcomment}[1]{\textcolor{Coquelicot}{\comment{Thomas: {#1}}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\title{Designing a Comparative Usability Study of Error Messages}
\date{April 23, 2016}

\begin{frame}
\frametitle{Designing a Comparative Usability Study of Error Messages}
{\centering
\noindent
Henry Fellows, Thomas Hagen, Sean Stockholm, \par
and Elena Machkasova \par

{\it 
Midwest Instruction and Computing Symposium\par
April 23, 2016\par}
}
\end{frame}
%frame

\begin{frame}
\frametitle{Table of contents}
\tableofcontents  
\end{frame}

\section{Introduction to the Project}

\begin{frame}
	\frametitle{Clojure in an introductory course}
	\begin{itemize}
		\item Developed in 2007 by Rich Hickey
		\item Member of the Lisp family
		\item Felleisen et al found Lisp languages to be useful in introductory courses
		\item Current UMM course uses a Lisp language
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Motivations for the project}
	\begin{itemize}
		\item ClojurEd
			\begin{itemize}
				\item ongoing project at UMM
				\item introduce Clojure in an introductory course
			\end{itemize}
		\item Our work focuses on error messages in Clojure
			\begin{itemize}
				\item error messages are a useful learning tool
				\item focus on usability
			\end{itemize}
	\end{itemize}
\end{frame}

\section{Overview of Clojure}

\begin{frame}
\frametitle{Overview of Clojure}
	\begin{itemize}
  	 \item Dynamically typed
  	 \item Data types immutable by default
  	 \item Functional
  	 \item Runs on the Java Virtual Machine (JVM)
  	 \item Read-eval-print-loop (REPL)
  	 	\begin{itemize}
  	 	\item interactive environment
  	 	\item useful for development and debugging
  	 	\end{itemize}
	 \end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Prefix notation}
	\begin{itemize}
  	  \item Clojure uses prefix notation
  	  \begin{itemize}
  	 	 \item parentheses
  	 	 \item parameters
  	 	 
  	 	 \texttt{(<function-name> <argument 1> <argument 2>)}
  	 	 \item \texttt{+} is a built-in function, not an operator
  	 	 \begin{verbatim}		
		 (+ 5 5)
		 -> 10
	     \end{verbatim}
	  \end{itemize}
   \end{itemize}
\end{frame}

\begin{frame}
\frametitle{Lisp}
\end{frame}

\begin{frame}
\frametitle{Lisp II}
\end{frame}

\begin{frame}
\frametitle{Differences between Racket and Clojure}
\end{frame}

\begin{frame}
\frametitle{Differences between Racket and Clojure II}
\end{frame}

\begin{frame}
\frametitle{Experimental Setup}
\end{frame}

\begin{frame}
\frametitle{Study Participation}
\end{frame}

\begin{frame}
\frametitle{Languages}
\end{frame}

\begin{frame}
\frametitle{Testing}
\end{frame}

\begin{frame}
\frametitle{Data Evaluation}
\end{frame}

\begin{frame}
\frametitle{Question Selection}
\end{frame}

\begin{frame}
	\frametitle{Meaningful & Accessible questions}
	\begin{itemize}
		\item The code examples should be simple enough to understand the programmer's intent with just a few test examples. 
		\item The code examples must have mistakes that a beginner programmer would make. Examples include switched arguments of a function or a mistyped identifier. 
		\item There must be a simple fix for an error. This is challenging since some errors, such as s type mismatch, can be caused by a variety of issues, and a beginner
	programmer can easily start making changes that are more complicated than they need to be, in an attempt to match the types. 
		\item Code examples and tests must use the same simple set of features in Racket and in Clojure. For instance, Racket uses a function \texttt{check-expect} for testing. Clojure also has a similar library (expectations), but it is more convoluted. Thus in order to equalize the experience in the two languages we chose to use only = and \texttt{equals?} function for testing since they are the same in the two languages. 
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Question parallelism}
\end{frame}


\begin{frame}
\frametitle{Question Selection}
\end{frame}


\begin{frame}
\frametitle{Examples}
\end{frame}

\begin{frame}
\frametitle{Examples}
\end{frame}

\begin{frame}
\frametitle{Conclusion}
	Never do a usability study on programming languages.
\end{frame}

\begin{frame}
\frametitle{Acknowledgments}
	Our research was sponsored by:
	\begin{itemize}
	\item HHMI
	\item UMN UROP
          \item Coginitect, Inc proivding funding for participants' compensation 
	\end{itemize}
	
	
	{\centering
	\noindent
	Thank you! \par
	Any questions? \par
	}
\end{frame}

\end{document}

